\bf Supervised Tensor Decomposition with Interactive Side Information

### 2020-09-17 tensor_regress/JASA_submission/paper_source/supp.tex
update

\usepackage{sectsty}
\sectionfont{\fontsize{12}{10}\selectfont}

@@

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
{\large\bf Supplementary Notes to ``Supervised Tensor Decomposition \\
with Interactive Side Information''}
\end{center}

@@

\section{Proofs}\label{sec:appedix}
\begin{proof}[Proof of Theorem~\ref{thm:main}]
Let $\sigma_{\text{min}}^{(k)} = \sigma_{\text{min}}(\mX_k)$ and  $\sigma_{\text{max}}^{(k)} = \sigma_{\text{max}}(\mX_k)$. First we prove \eqref{eq:bound}. 
Define $\ell(\tB)=\mathbb{E}(\tL_{\tY}(\tB))$, where the expectation is taken with respect to $\tY\sim \trueB$ under the model with true parameter $\trueB$. We prove the following two conclusions:
\begin{enumerate}
\item[C1.] There exist two positive constants $C_1$, $C_2>0$, such that, with probability at least $1-\exp(-C_1\log K\sum_k p_k)$, the stochastic deviation, $\tL_{\tY}(\tB)-\ell(\tB)$, satisfies
\[
|\tL_{\tY}(\tB)-\ell(\tB)|=|\langle \tE,\ \tB\times_1\mX_1\times_2\cdots\times_K \mX_K\rangle| \leq C_2\FnormSize{}{\tB} \left(\prod_k \sigma_{\text{max}}^{(k)}\right)\sqrt{{\prod_k r_k \over \max_k r_k} \sum_k p_k}.
\]
\item[C2.] The inequality $\ell(\hat \tB) - \ell(\trueB) \leq  -{L\over 2}\FnormSize{}{\hat \Theta-\trueT}^2$ holds, where $L>0$ is the lower bound for $\min_{|\theta|\leq \alpha}|b''(\theta)|$. 
\end{enumerate}

@@

We take expectation with respect to $\tY\sim \trueB$ on both sides of~\eqref{eq:log} and obtain
\begin{equation}\label{eq:log}
\ell(\tB)=\ell(\trueB)+{1\over 2}\text{vec}(\tB-\trueB)^T \tH(\check \tB)\text{vec}(\tB-\trueB).
\end{equation}
By the fact ${\partial \tL_{\tY}^2(\Theta)\over \partial^2 \Theta}=-b''(\Theta)$ and chain rule over $\Theta=\Theta(\tB)=\tB\times_1\mX_1\cdots\times_K\mX_K$, the equation~\eqref{eq:log} implies that 
\begin{equation}\label{eq:logB}
\ell(\tB)-\ell(\trueB)=-{1\over 2}\sum_{i_1,\ldots,i_K}b''(\check \theta_{i_1,\ldots,i_K}) (\theta_{i_1,\ldots,i_K}-\theta_{\text{true},i_1,\ldots,i_K})^2 \leq -{L \over 2}\FnormSize{}{\Theta-\trueT}^2,
\end{equation}
holds for all $\tB\in\tP$, provided that $\min_{|\theta|\leq \alpha}|b''(\theta)|\geq L>0$. In particular, the inequality~\eqref{eq:log} also applies to the constrained MLE $\hat \tB$. So we have
\begin{equation}\label{upper}
\ell(\hat \tB)-\ell(\trueB)\leq -{L \over 2}\FnormSize{}{\hat \Theta-\trueT}^2.
\end{equation}
Now we have proved both C1 and C2. Note that $\tL_{\tY}(\hat \tB)- \tL_{\tY}(\trueB)\geq 0$ by the definition of $\hat \tB$, This implies that
\begin{align}
0&\leq \tL_{\tY}(\hat \tB)- \tL_{\tY}(\trueB) \\
&\leq \left(\tL_{\tY}(\hat \tB)-\ell(\hat \tB)\right)-\left( \tL_{\tY}(\trueB)-\ell(\trueB)\right)+\left(\ell(\hat \tB)-\ell(\trueB)\right)\\
&\leq \langle\tE,\ \Theta-\trueT    \rangle -{L\over 2}\FnormSize{}{\hat \Theta-\trueT}^2,
\end{align}
where the second line follows from~\eqref{upper}. Therefore,
\begin{align}\label{eq:1}
\FnormSize{}{\hat \Theta-\trueT}&\leq {2\over L}\big\langle \tE,\ {\hat \Theta -\trueT \over \FnormSize{}{\hat \Theta-\trueT}} \big\rangle\notag \\
&\leq {2\over L}\sup_{\Theta: \FnormSize{}{\Theta}=1, \Theta=\tB\times_1\mX_1\times_2\cdots\times_K \mX_K}\langle \tE,\ \Theta \rangle\notag \\
&\leq {2\over L}\sup_{\tB\in\tP: \FnormSize{}{\tB}\leq \left(\prod_k \sigma_{\min}^{(k)}\right)^{-1}} \langle \tE,\ \ \tB\times_1\mX_1\times_2\cdots\times_K\mX_K\rangle.
\end{align}
Combining~\eqref{eq:1} with C1 yields 
\begin{align}\label{eq:theta}
\FnormSize{}{\hat \Theta-\trueT} \leq {2C_2\over L} \frac{\prod_k \sigma_{\max}^{(k)}}{\prod_k \sigma_{\min}^{(k)}}\sqrt{{\prod_k r_k \over \max r_k}\sum_k p_k}.
\end{align}
Therefore,
\begin{equation}\label{eq:Bbound}
\FnormSize{}{\hat \tB-\trueB}\leq \FnormSize{}{\hat \Theta-\trueT}\left(\prod_k \sigma_{\min}^{(k)}\right)^{-1}\leq {2C_2\over L} \frac{\prod_k \sigma_{\max}^{(k)}}{\left(\prod_k \sigma_{\min}^{(k)}\right)^2}\sqrt{{\prod_k r_k \over \max r_k}\sum_k p_k}.
\end{equation}
We now consider the two cases of assumptions on the feature matrices. 
\begin{itemize}[leftmargin=0cm]
\item[] [Case 1] Under Assumption A1 with scaled feature matrices, we have the singular value
\begin{equation}\label{eq:case1}
\frac{\prod_k \sigma_{\max}^{(k)}}{\left(\prod_k \sigma_{\min}^{(k)}\right)^2} = {\prod_k c_2\sqrt{d_k}\over \left(\prod_k c_1\sqrt{d_k}\right)^2}.
\end{equation}
\item[] [Case 2] Under Assumption A1', we have asymptotic behavior of extreme singular values  \citep{rudelson2010non} as 
\[
\sigma_{\text{min}}^{(k)} \sim \sqrt{d_k}-\sqrt{p_k} \text{ and  } \sigma_{\text{max}}^{(k)} \sim \sqrt{d_k}+\sqrt{p_k}.
\]
In this case, we obtain 
\begin{equation}\label{eq:case2}
\frac{\prod_k \sigma_{\max}^{(k)}}{\left(\prod_k \sigma_{\min}^{(k)}\right)^2} = {\prod_k (\sqrt{d_k}+\sqrt{p_k})\over \prod_k (\sqrt{d_k}-\sqrt{p_k})^2} =\frac{\prod_k(1+\sqrt{\gamma_k})\sqrt{d_k}}{\prod_k(1-\sqrt{\gamma_k})^2d_k}.
\end{equation}
\end{itemize}
Combining~\eqref{eq:Bbound} with either~\eqref{eq:case1} or~\eqref{eq:case2}, we obtain the same conclusion in both cases,
\[
\FnormSize{}{\hat \tB-\trueB}^2\leq \frac{ C_{2} r_{\textup{total}}}{r_{\max}}\frac{\sum_k p_k}{\prod_k d_k},
\]
where $C_2=C_2(\alpha,K,c_1, c_2)>0$ in the first case and $C_2=C_2(\alpha,K,\gamma)>0$ in the second case, both of which are constants that do not depend on the dimensions $\{d_k\}$ and $\{p_k\}$.

Now we prove \eqref{eq:sinebound}.
We unfold tensors $\trueB$ and $\hat\tB$ along the mode $k$ and obtain $\text{Unfold}_k(\trueB)$ and $\text{Unfold}_k(\hat\tB)$. Notice that 
\begin{align}
    \text{Unfold}_k(\trueB) &= \mM_k \text{Unfold}_k(\trueC)\left(\mM_{k+1}\otimes\mM_{k+2}\otimes \cdots\otimes \mM_1\otimes \cdots\mM_{k-1}\right)^T,\\
    \text{Unfold}_k(\hat\tB) &= \hat\mM_k \text{Unfold}_k(\hat\tC)\left(\hat\mM_{k+1}\otimes\hat\mM_{k+2}\otimes \cdots\otimes \hat\mM_1\otimes \cdots\hat\mM_{k-1}\right)^T,
\end{align} where $\otimes$ denotes the Kronecker product of matrices.
Notice that $\mM_k$ and $\hat\mM_k$ have the same image of left singular matrices of $\text{Unfold}_k(\trueB)$ and $\text{Unfold}_k(\hat\tB)$ respectively.  Applying Proposition \ref{prop:sinebound}, we have
\begin{align}
    \text{sin}\Theta^2(\mM_k,\hat\mM_k)\leq \frac{\FnormSize{}{\text{Unfold}_k(\hat\tB)-\text{Unfold}_k(\trueB)}}{\sigma_{\text{min}}(\text{Unfold}_k(\trueB))}= \frac{\FnormSize{}{\hat\tB-\trueB}}{\sigma_{\text{min}}(\text{Unfold}_k(\trueC))},
\end{align} where $\sigma_{\text{min}}(\text{Unfold}_k(\trueB)) = \sigma_{\text{min}}(\text{Unfold}_k(\trueC))$ holds based on the orthonormality of factor matrices. We finally prove \eqref{eq:sinebound} combining \eqref{eq:bound}.
\end{proof}

@@

\begin{prop}[Wedin's $\sin\Theta$ Theorem]\label{prop:sinebound}
Let $\mB$ and $\hat\mB$ be two $m\times n$ real or complex with SVDs $\mB = \mU\Sigma\mV^T$ and $\hat\mB = \hat\mU\hat\mSigma\hat\mV^T.$ If $\sigma_{\text{min}}(\mB)>0$ and $\FnormSize{}{\hat\mB-\mB}\ll \sigma_{\text{min}}(\mB)$, then
\begin{align}\label{eq:sine}
    \text{sin}\Theta(\mU,\hat\mU) \leq \frac{C\FnormSize{}{\hat\mB-\mB}}{\sigma_{\text{min}}(\mB)},
\end{align}
for some constant $C>0$.
\end{prop}
\begin{proof}
From Theorem 6.1 in \cite{wang2017tensor}, we  obtain the following bound 
\begin{align}
    \max\left\{\snormSize{}{\text{sin}\Theta(\mU,\hat\mU)},\snormSize{}{\text{sin}\Theta(\mV,\hat\mV)}\right\}\leq \frac{\max\left\{\snormSize{}{\hat\mB\mV-\mU\mSigma},\snormSize{}{\hat\mB^T\mU-\mV\mSigma}\right\}}{\sigma_{\text{min}}(\mB)}.
\end{align}
Notice that
\begin{align}
    \snormSize{}{\hat\mB\mV-\mU\mSigma} &= \snormSize{}{\hat\mB\mV-\mB\mV} = \snormSize{}{\hat\mB-\mB} \leq \FnormSize{}{\hat\mB-\mB},\\
    \snormSize{}{\hat\mB^T\mU-\mV\mSigma} &= \snormSize{}{\hat\mB^T\mU-\mB^T\mU} = \snormSize{}{\hat\mB-\mB} \leq \FnormSize{}{\hat\mB-\mB}.
\end{align}
Therefore,we prove \eqref{eq:sine}.
\end{proof}

@@

\newpage
\section{Additional simulation results}
Section~\ref{sec:simulation} in the main text has provided simulation results for two settings: low-signal, high-rank setting and high-signal, low-rank setting. Here, we perform the simulations for the full combinations of rank $\mr=(3,3,3), (4,5,6)$ and signal $\alpha=3, 6$. Figures~\ref{fig:S1} and~\ref{fig:S2} confirm the outperformance of the supervised tensor method in a range of model complexities.

\begin{figure}[!h]
\centering
\includegraphics[width=16cm]{Supp_Figure1.pdf} 
\caption{Comparison of MSPE versus the number of modes with features. We consider full combinations of rank $\mr=(3,3,3)$ (low), $\mr=(4,5,6)$ (high), and signal $\alpha=3$ (low), $\alpha=6$ (high).}~\label{fig:S1}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=16cm]{Supp_Figure2.pdf} 
\caption{Comparison of MSPE versus effective sample size. We consider full combinations rank $\mr=(3,3,3)$ (low), $\mr=(4,5,6)$ (high), and signal $\alpha=3$ (low), $\alpha=6$ (high). }~\label{fig:S2}
\end{figure}

\bibliography{tensor_wang}
\bibliographystyle{apalike}

>>>>

@@

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
{\Large\bf Supplementary Notes to ``Supervised Tensor Decomposition
with Interactive Side Information''}
\end{center}

@@

\section{Proofs}\label{sec:appedix}
We restate the Theorem 4.1 from the main text. 
 \begin{thm}[Statistical convergence]\label{thm:main}
Consider a data tensor generated from model~\eqref{eq:decomp}, where the entries are conditionally independent realizations from an exponential family. Let $(\hat \tC, \hat \mM_1,\ldots,\hat \mM_K)$ be the M-estimator in~\eqref{eq:MLE} and $\hat \tB=\hat \tC\times \hat \mM_1\times\cdots \times \hat \mM_K$. Define $r_\textup{total}=\prod_k r_k$ and $r_{\max}=\max_k r_k$. Under Assumptions A1 and A2 with scaled feature matrices $\check \mX_k= \sqrt{d_k}\mX_k$, or under Assumptions A1' and A2 with original feature matrices, there exist two positive constants $C_1=C_1(\alpha,K), C_2=C_2(\alpha, K)>0$ independent of dimensions $\{d_k\}$ and $\{p_k\}$, such that, with probability at least $1-\exp(-C_1\sum_k p_k)$, 
\begin{equation}\label{eq:bound}
    \FnormSize{}{\trueB- \hat \tB}^2\leq \frac{ C_{2} r_{\textup{total}}}{r_{\max}}\frac{\sum_k p_k}{\prod_k d_k}.
\end{equation}
Furthermore, if the unfolded core tensor has non-degenerate singular values at mode $k\in[K]$, i.e., $\sigma_{\min}(\textup{Unfold}_k(\tC_\textup{true})) \geq c>0$ for some constant $c$, then
\begin{equation}\label{eq:sinebound}
\textup{sin}^2 \Theta(\trueM,\ \hat \mM_k) \leq  \frac{ C_{2}r_{\textup{total}}}{ r_{\max}\sigma^2_{\min}(\textup{Unfold}_k(\tC_\textup{true}))}\frac{\sum_k p_k}{\prod_k d_k}.
\end{equation}
\end{thm}

\begin{proof}[Proof of Theorem~\ref{thm:main}]
Let $\sigma_{\text{min}}^{(k)} = \sigma_{\text{min}}(\mX_k)$ and  $\sigma_{\text{max}}^{(k)} = \sigma_{\text{max}}(\mX_k)$. First we prove \eqref{eq:bound}. 
Define $\ell(\tB)=\mathbb{E}(\tL_{\tY}(\tB))$, where the expectation is taken with respect to $\tY\sim \trueB$ under the model with true parameter $\trueB$. We prove the following two conclusions:
\begin{enumerate}
\item[C1.] There exist two positive constants $C_1$, $C_2>0$, such that, with probability at least $1-\exp(-C_1\log K\sum_k p_k)$, the stochastic deviation, $\tL_{\tY}(\tB)-\ell(\tB)$, satisfies
\[
|\tL_{\tY}(\tB)-\ell(\tB)|=|\langle \tE,\ \tB\times_1\mX_1\times_2\cdots\times_K \mX_K\rangle| \leq C_2\FnormSize{}{\tB} \left(\prod_k \sigma_{\text{max}}^{(k)}\right)\sqrt{{\prod_k r_k \over \max_k r_k} \sum_k p_k}.
\]
\item[C2.] The inequality $\ell(\hat \tB) - \ell(\trueB) \leq  -{L\over 2}\FnormSize{}{\hat \Theta-\trueT}^2$ holds, where $L>0$ is the lower bound for $\min_{|\theta|\leq \alpha}|b''(\theta)|$. 
\end{enumerate}

@@

We take expectation with respect to $\tY\sim \trueB$ on both sides of~\eqref{eq:log} and obtain
\begin{equation}\label{eq:log}
\ell(\tB)=\ell(\trueB)+{1\over 2}\text{vec}(\tB-\trueB)^T \tH(\check \tB)\text{vec}(\tB-\trueB).
\end{equation}
By the fact ${\partial \tL_{\tY}^2(\Theta)\over \partial^2 \Theta}=-b''(\Theta)$ and chain rule over $\Theta=\Theta(\tB)=\tB\times_1\mX_1\cdots\times_K\mX_K$, the equation~\eqref{eq:log} implies that 
\begin{equation}\label{eq:logB}
\ell(\tB)-\ell(\trueB)=-{1\over 2}\sum_{i_1,\ldots,i_K}b''(\check \theta_{i_1,\ldots,i_K}) (\theta_{i_1,\ldots,i_K}-\theta_{\text{true},i_1,\ldots,i_K})^2 \leq -{L \over 2}\FnormSize{}{\Theta-\trueT}^2,
\end{equation}
holds for all $\tB\in\tP$, provided that $\min_{|\theta|\leq \alpha}|b''(\theta)|\geq L>0$. In particular, the inequality~\eqref{eq:log} also applies to the constrained MLE $\hat \tB$. So we have
\begin{equation}\label{upper}
\ell(\hat \tB)-\ell(\trueB)\leq -{L \over 2}\FnormSize{}{\hat \Theta-\trueT}^2.
\end{equation}
Now we have proved both C1 and C2. Note that $\tL_{\tY}(\hat \tB)- \tL_{\tY}(\trueB)\geq 0$ by the definition of $\hat \tB$. This implies that
\begin{align}\label{eq:F-norm}
0&\leq \tL_{\tY}(\hat \tB)- \tL_{\tY}(\trueB) \\
&\leq \left(\tL_{\tY}(\hat \tB)-\ell(\hat \tB)\right)-\left( \tL_{\tY}(\trueB)-\ell(\trueB)\right)+\left(\ell(\hat \tB)-\ell(\trueB)\right)\\
&\leq \langle\tE,\ \Theta-\trueT    \rangle -{L\over 2}\FnormSize{}{\hat \Theta-\trueT}^2,
\end{align}
where the second line follows from~\eqref{upper}.

The inequality~\eqref{eq:F-norm} can be rewritten as
\begin{align}\label{eq:1}
\FnormSize{}{\hat \Theta-\trueT}&\leq {2\over L}\big\langle \tE,\ {\hat \Theta -\trueT \over \FnormSize{}{\hat \Theta-\trueT}} \big\rangle\notag \\
&\leq {2\over L}\sup_{\Theta: \FnormSize{}{\Theta}=1, \Theta=\tB\times_1\mX_1\times_2\cdots\times_K \mX_K}\langle \tE,\ \Theta \rangle\notag \\
&\leq {2\over L}\sup_{\tB\in\tP: \FnormSize{}{\tB}\leq \left(\prod_k \sigma_{\min}^{(k)}\right)^{-1}} \langle \tE,\ \ \tB\times_1\mX_1\times_2\cdots\times_K\mX_K\rangle.
\end{align}
Combining~\eqref{eq:1} with C1 yields 
\begin{align}\label{eq:theta}
\FnormSize{}{\hat \Theta-\trueT} \leq {2C_2\over L} \frac{\prod_k \sigma_{\max}^{(k)}}{\prod_k \sigma_{\min}^{(k)}}\sqrt{{\prod_k r_k \over \max r_k}\sum_k p_k}.
\end{align}
Therefore,
\begin{equation}\label{eq:Bbound}
\FnormSize{}{\hat \tB-\trueB}\leq \FnormSize{}{\hat \Theta-\trueT}\left(\prod_k \sigma_{\min}^{(k)}\right)^{-1}\leq {2C_2\over L} \frac{\prod_k \sigma_{\max}^{(k)}}{\left(\prod_k \sigma_{\min}^{(k)}\right)^2}\sqrt{{\prod_k r_k \over \max r_k}\sum_k p_k}.
\end{equation}
We now consider the two cases of assumptions on the feature matrices. 
\begin{itemize}[leftmargin=0cm]
\item[] [Case 1] Under Assumption A1 with scaled feature matrices, we have the singular value
\begin{equation}\label{eq:case1}
\frac{\prod_k \sigma_{\max}^{(k)}}{\left(\prod_k \sigma_{\min}^{(k)}\right)^2} = {\prod_k c_2\sqrt{d_k}\over \left(\prod_k c_1\sqrt{d_k}\right)^2}.
\end{equation}
\item[] [Case 2] Under Assumption A1', we have asymptotic behavior of extreme singular values \citep{rudelson2010non} as 
\[
\sigma_{\text{min}}^{(k)} \sim \sqrt{d_k}-\sqrt{p_k} \text{ and  } \sigma_{\text{max}}^{(k)} \sim \sqrt{d_k}+\sqrt{p_k}.
\]
In this case, we obtain 
\begin{equation}\label{eq:case2}
\frac{\prod_k \sigma_{\max}^{(k)}}{\left(\prod_k \sigma_{\min}^{(k)}\right)^2} = {\prod_k (\sqrt{d_k}+\sqrt{p_k})\over \prod_k (\sqrt{d_k}-\sqrt{p_k})^2} =\frac{\prod_k(1+\sqrt{\gamma_k})\sqrt{d_k}}{\prod_k(1-\sqrt{\gamma_k})^2d_k}.
\end{equation}
\end{itemize}
Combining~\eqref{eq:Bbound} with either~\eqref{eq:case1} or~\eqref{eq:case2}, we obtain the same conclusion in both cases,
\[
\FnormSize{}{\hat \tB-\trueB}^2\leq \frac{ C_{2} r_{\textup{total}}}{r_{\max}}\frac{\sum_k p_k}{\prod_k d_k},
\]
where $C_2=C_2(\alpha,K,c_1, c_2)>0$ in the first case and $C_2=C_2(\alpha,K,\gamma)>0$ in the second case, both of which are constants that do not depend on the dimensions $\{d_k\}$ and $\{p_k\}$.

Now we prove bound for sin$\Theta$ distance. 
We unfold tensors $\trueB$ and $\hat\tB$ along the mode $k$ and obtain $\text{Unfold}_k(\trueB)$ and $\text{Unfold}_k(\hat\tB)$. Notice that 
\begin{align}
    \text{Unfold}_k(\trueB) &= \mM_k \text{Unfold}_k(\trueC)\left(\mM_{k+1}\otimes\mM_{k+2}\otimes \cdots\otimes \mM_1\otimes \cdots\mM_{k-1}\right)^T,\\
    \text{Unfold}_k(\hat\tB) &= \hat\mM_k \text{Unfold}_k(\hat\tC)\left(\hat\mM_{k+1}\otimes\hat\mM_{k+2}\otimes \cdots\otimes \hat\mM_1\otimes \cdots\hat\mM_{k-1}\right)^T,
\end{align} where $\otimes$ denotes the Kronecker product of matrices.
Notice that $\mM_k$ and $\hat\mM_k$ have the same image of left singular matrices of $\text{Unfold}_k(\trueB)$ and $\text{Unfold}_k(\hat\tB)$ respectively.  Applying Proposition \ref{prop:sinebound}, we have
\begin{align}\label{eq:sintheta}
    \text{sin}^2\Theta(\mM_k,\hat\mM_k)\leq \frac{\FnormSize{}{\text{Unfold}_k(\hat\tB)-\text{Unfold}_k(\trueB)}}{\sigma_{\text{min}}(\text{Unfold}_k(\trueB))}= \frac{\FnormSize{}{\hat\tB-\trueB}}{\sigma_{\text{min}}(\text{Unfold}_k(\trueC))},
\end{align} where $\sigma_{\text{min}}(\text{Unfold}_k(\trueB)) = \sigma_{\text{min}}(\text{Unfold}_k(\trueC))$ holds based on the orthonormality of factor matrices. We finally prove the sin$\Theta$ distance by combining~\eqref{eq:sintheta} and \eqref{eq:bound}.
\end{proof}

@@

\begin{prop}[Wedin's $\sin\Theta$ Theorem]\label{prop:sinebound}
Let $\mB$ and $\hat\mB$ be two $m\times n$ real or complex with SVDs $\mB = \mU\Sigma\mV^T$ and $\hat\mB = \hat\mU\hat\mSigma\hat\mV^T.$ If $\sigma_{\text{min}}(\mB)>0$ and $\FnormSize{}{\hat\mB-\mB}\ll \sigma_{\text{min}}(\mB)$, then
\begin{align}\label{eq:sine}
    \text{sin} \Theta(\mU,\hat\mU) \leq \frac{\FnormSize{}{\hat\mB-\mB}}{\sigma_{\text{min}}(\mB)}.
\end{align}

\end{prop}
\begin{proof}
From Theorem 6.1 in \cite{wang2017tensor}, we  obtain the following bound 
\begin{align}
    \max\left\{\snormSize{}{\text{sin}\Theta(\mU,\hat\mU)},\snormSize{}{\text{sin}\Theta(\mV,\hat\mV)}\right\}\leq \frac{\max\left\{\snormSize{}{\hat\mB\mV-\mU\mSigma},\snormSize{}{\hat\mB^T\mU-\mV\mSigma}\right\}}{\sigma_{\text{min}}(\mB)}.
\end{align}
Notice that
\begin{align}
    \snormSize{}{\hat\mB\mV-\mU\mSigma} &= \snormSize{}{\hat\mB\mV-\mB\mV} = \snormSize{}{\hat\mB-\mB} \leq \FnormSize{}{\hat\mB-\mB},\\
    \snormSize{}{\hat\mB^T\mU-\mV\mSigma} &= \snormSize{}{\hat\mB^T\mU-\mB^T\mU} = \snormSize{}{\hat\mB-\mB} \leq \FnormSize{}{\hat\mB-\mB}.
\end{align}
Therefore, we prove \eqref{eq:sine}.
\end{proof}

@@

\section{Computational complexity}
The computational complexity of our Algorithm~\eqref{alg:B} is $O\left(d \sum_k p^3_k\right)$ for each loop of iterations, where $d=\prod_k d_k$ is the total size of the data tensor. More precisely, the update of core tensor costs $O(r^3d)$, where $r=\prod_k r_k$ is the total size of the core tensor. The update of each factor matrix $\mM_k$ involves a GLM with a $d$-length response, and $d$-by-$(r_kp_k)$ feature matrix. Solving such a GLM requires $O(dr^3_kp^3_k)$, and therefore the cost for updating $K$ factors in total is $O( d\sum_k r^3_k p_k^3)$. This complexity in tensor dimension matches with the classical tensor decomposition~\citep{kolda2009tensor}.

\section{Additional simulation results}
Section~\ref{sec:simulation} in the main text has provided simulation results for two settings: low-signal, high-rank setting and high-signal, low-rank setting. Here, we perform the simulations for the full combinations of rank $\mr=(3,3,3), (4,5,6)$ and signal $\alpha=3, 6$. Figures~\ref{fig:S1} and~\ref{fig:S2} confirm the outperformance of the supervised tensor method in a range of model complexities.

\begin{figure}[H]
\centering
\includegraphics[width=15cm]{Supp_Figure1.pdf} 
\caption{Comparison of MSPE versus the number of modes with features. We consider full combinations of rank $\mr=(3,3,3)$ (low), $\mr=(4,5,6)$ (high), and signal $\alpha=3$ (low), $\alpha=6$ (high).}~\label{fig:S1}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=15cm]{Supp_Figure2.pdf} 
\caption{Comparison of MSPE versus effective sample size. We consider full combinations rank $\mr=(3,3,3)$ (low), $\mr=(4,5,6)$ (high), and signal $\alpha=3$ (low), $\alpha=6$ (high). }~\label{fig:S2}
\end{figure}

\newpage
\bibliography{tensor_wang}
\bibliographystyle{apalike}
